\irsection{Obtaining, placing, and editing the module files}{ModuleFiles}

For a user internal to Illinois Rocstar the files necessary for building a module for \elmer can be found in the source repository under \irfilename{svn://irsvn/SourceRepository/MPInfra/Third\_Party\_ Modules/ElmerTest/trunk}. For an external user these files may be found on the open multiphysics website (to come). The files will contain the appropriate directory structure for building the driver. However, the files used with \elmer to create a module library must be placed in the appropriate locations within the \elmer source files in order for them to build. These files are located under the \irfilename{native} directory of the module main source directory. The locations for placing these files will be given, but it should be noted that these are specific for \elmer \software{7.0}. In the case of another version of \elmer\!\!, it may be necessary to place these files in different locations. If you are using a different version of \elmer\!\!, it is suggested that you locate the source file \irfilename{Solver.src} and then place the module files in a manner with a similar structure to that shown here. 

All paths below are shown from within the \elmer main source directory.

\begin{itemize}
\item The main source file \irfilename{Solver.src} should be located under \irfilename{fem/src}.
\item Place \irfilename{SolverModuleHeader.H}, \irfilename{SolverModule.src}, and \irfilename{ModTestObject.f90} in \irfilename{fem/src}.
\item Add the contents from \irfilename{CMakeLists\_Additions.txt} to the bottom of the \irfilename{CMakeLists.txt} file in \irfilename{fem/src}.
\end{itemize}

The module files are now in place and \irfilename{CMakeLists.txt} edited, so the module library can be built.

